密文重复数据删除机制的频率攻击方法

### 2019-01-03 paper/Experiments.tex
ING | complete chapter 4 and begin chapter 5 before workflow
ING | Clustering Attack
ING | last part - exp - figure fix

In this section, we present the trace-driven evaluation results to demonstrate
the severity of our proposed frequency analysis attacks against encrypted
deduplication.

@@

\begin{table}[!t]
    \caption{Characteristics of experimental datasets.}
\small
\label{tab:dataset}
\renewcommand{\arraystretch}{1.2}
\vspace{-3pt}
\centering
\begin{tabular}{|c|c|c|c|}
\hline
 \multirow{2}{*}{\bf Dataset} & \multirow{2}{*}{\bf Category} & \multicolumn{2}{c|}{\bf Characteristics in Each Snapshot} \\
\cline{3-4}
    & &  \#Logical (Million) & \#Unique (Million) \\
\hline
    \multirow{6}{*}{FSL} & User004  & 1.0-1.3 & 0.7-0.9\\
 \cline{2-4}
              & User007 &  3.5-5.2 & 2.3-3.6 \\
 \cline{2-4}
              & User012 &  25.0-26.4 & 8.9-9.7 \\
\cline{2-4}
              & User013 &  1.8-5.7 & 1.2-4.2 \\
\cline{2-4}
              & User015 &  13.4-20.5 & 9.0-11.0 \\
\cline{2-4}
              & User028 &  6.0-10.3 & 3.5-6.8 \\
\hline
\hline
    \multirow{4}{*}{MS} & Win7  & 61.6-61.8 & 61.1-61.3\\
\cline{2-4}
              & Serv-03 & 10.6-10.7 & 8.4-8.5\\
\cline{2-4}
              & Serv-08 & $\sim$6.5 & $\sim$3.8 \\
\cline{2-4}
              & Vista-B &  $\sim$7.6 & $\sim$2.0\\
\cline{2-4}
              & Vista-U &  $\sim$21.0 & $\sim$10.4 \\
\hline
\hline

    \multirow{6}{*}{VM} & User1  &  \multirow{6}{*}{2.6} & $\sim$0.9 \\
\cline{2-2}
\cline{4-4}
              & User2 &  & 1.1-1.3 \\
\cline{2-2}
\cline{4-4}
              & User3 &  & 0.9-1.1 \\
\cline{2-2}
\cline{4-4}
              & User4 &  & $\sim$0.9 \\
\cline{2-2}
\cline{4-4}
              & User5 &  & 0.9-1.0 \\
\cline{2-2}
\cline{4-4}
              & User6 &  & 0.9-1.1 \\
\hline
\end{tabular}
\medskip

\raggedright
    The notations \#Logical and \#Unique denote the total number of logical and unique chunks in each experimental snapshot, respectively. 
    % All VM images have a fixed size of 10GB and hence the same number of logical chunks.
\end{table}

%\begin{table}[!t]
%\small
%\caption{Experimental datasets.}
%\label{tab:dataset}
%\renewcommand{\arraystretch}{1.2}
%\vspace{-3pt}
%\centering
%\begin{tabular}{|c|c|c|}
%\hline
%{\bf Dataset} & {\bf Category} & {\bf Approximate Logical Size} \\
%\hline
%\hline
%%\multirow{2}{*}{FSL} & Physical  & 431.9GB  & 659.3GB & 584.3GB \\
%	\multirow{6}{*}{FSL} & User004  & 10GB/backup $\times$ 14 backups \\
%\cline{2-3}
%			  & User007 & 39GB/backup $\times$ 14 backups \\
%\cline{2-3}
%			  & User012 & 244GB/backup $\times$ 14 backups \\
%\cline{2-3}
%			  & User013 & 22GB/backup $\times$ 14 backups\\
%\cline{2-3}
%			  & User015 & 158GB/backup $\times$ 14 backups\\
%\cline{2-3}
%			  & User028 & 77GB/backup $\times$ 14 backups\\
%\hline
%\hline
%\multirow{4}{*}{MS} & WIN7  & 425GB/snapshot $\times$ 4 snapshots \\
%\cline{2-3}
%			  & Serv-03 & 78GB/snapshot $\times$ 4 snapshots \\
%\cline{2-3}
%			  & Serv-08 & 48GB/snapshot $\times$ 4 snapshots \\
%\cline{2-3}
%			  & Vista-B & 55GB/snapshot $\times$ 4 snapshots \\
%\cline{2-3}
%			  & Vista-U & 159GB/snapshot $\times$ 4 snapshots \\

%\hline
%\hline

%\multirow{6}{*}{VM} & User1  & 25GB/backup $\times$ 13 backups \\
%\cline{2-3}
%			  & User2 & 28GB/backup $\times$ 13 backups \\
%\cline{2-3}
%			  & User3 & 26GB/backup $\times$ 13 backups \\
%\cline{2-3}
%			  & User4 & 25GB/backup $\times$ 13 backups\\
%\cline{2-3}
%			  & User5 & 25GB/backup $\times$ 13 backups\\
%\cline{2-3}
%			  & User6 & 27GB/backup $\times$ 13 backups\\

%% \multicolumn{2}{|c|}{\bf Storage saving} & 98.6\% & 98.3\% \\
%\hline
%\end{tabular}
%\end{table}
We evaluate our attacks using the following real-world datasets, whose
characteristics are summarized in Table~\ref{tab:dataset}. 
% Table~\ref{tab:dataset} summarizes the characteristics of the experimental datasets used in our experiments. 
% We evaluate our attacks using the following datasets. 
% investigate the security implications of the leakages (see \S\ref{sec:background}) by means of simulated attacks,

\begin{itemize}[leftmargin=*]
\item 
\textbf{FSL:} This dataset is collected by the File systems and
        Storage Lab (FSL) at Stony Brook University \cite{sun16,FSL14,sun18}. We focus on
the {\em fslhomes} snapshots, each of which includes an ordered list of 48-bit
chunk hashes that are produced by variable-size chunking under an average size
of 8KB, as well as the corresponding metadata information (e.g., chunk size,
file name extension, etc). We pick the snapshots from January 22 to May 21 in
2013, and select six users (i.e., User004, User007, User012, User013, User015,
and User028) that have the complete daily snapshots over the whole duration.
We collect these snapshots on a weekly basis, and hence form 14 weekly full
backups for each user.  
\item 
\textbf{MS:} This dataset is collected by Microsoft
\cite{meyer11} and publicized on SNIA \cite{ms}. The original dataset contains
the Windows file system snapshots that span from September 5 to October 31,
2009. Each snapshot is represented by the 40-bit chunk hashes under different
average sizes obtained from Rabin fingerprinting \cite{rabin81}.  We focus on
the snapshots that have been installed with the operating systems in the
following categories: Windows 7 (Win7), Microsoft Windows Server 2003
(Serv-03), Microsoft Windows Server 2008 (Serv-08), Microsoft Windows Vista
Business Edition (Vista-B), and Microsoft Windows Vista Ultimate Edition
(Vista-U). In each category, we pick four snapshots, each of which is
configured with the average chunk size of 8KB.   
\item 
\textbf{VM:} This dataset is collected from a university programming course in
Spring 2014. The original dataset includes a number of VM image snapshots for
the students enrolled in the course, and each snapshot has a fixed size of
10GB and is represented by the ordered list of SHA-1 hashes of 4KB fixed-size
chunks. We focus on 6 users (i.e., User1-User6) and extract their snapshots
into 13 weekly backups.  
%Prior studies \cite{qin17, li15} have used some variants of the dataset for
%different evaluation purposes, and we aim to validate the severity of the
%clustering-based attack against VM disk images.   
\end{itemize}

@@

% , although we cannot recover each chunk in the real attack.   
% We count the leakage (see \S\ref{sec:threat}) of each ciphertext chunk, and use it for our inference attacks.  
% MD5 on each hash (that represents a plaintext) in $\mathbf{M}$, and truncate the resulting hash into an agreed number of bits (e.g., 48-bit for FSL, 40-bit for MS, and 160-bit for VM).

@@

\begin{figure*}[t]
    \centering
    \begin{tabular}{p{.31\textwidth}p{.31\textwidth}p{.31\textwidth}}
        \multicolumn{3}{c}{\includegraphics[width=.7\textwidth]{pic/legend-fsl-line.pdf}} \smallskip \\
        \includegraphics[width=.3\textwidth]{pic/distribution-impact-u.pdf} &
        \includegraphics[width=.3\textwidth]{pic/distribution-impact-r.pdf} &
	    \includegraphics[width=.3\textwidth]{pic/distribution-impact-t.pdf} \medskip \\
        {\footnotesize 
        \centering
        (a) Impact of $u$: $r$ = 0; $t \rightarrow \infty$
        } &
        {\footnotesize
        (b) Impact of $r$: $u$ = 128 for User004, User013 and User015, and $u$ = 256 for User007, User012 and User028; $t \rightarrow \infty$
        } &
        {\footnotesize
        (c) Impact of $t$: $u$ = 128 for User004, User013 and User015, and $u$ = 256 for User007, User012 and User028; $r$ = 10
        } \\
    \end{tabular}
    \caption{Experiment 1 (Impact of parameters): impact of $(u, r, t)$ in distribution-based attack.}
    \label{fig:distribution-impact}
\end{figure*}

@@

The prior work \cite{li17} does not report the inference precision about the
attack. We observe that the inference precisions for all users are at a
fairly low level (e.g., less than 40\%), except the case of $u = 2$ for
User028 that does not introduce any false positives. On the other hand, the
inference rate in the special case is about 0.0001\%, meaning that the attack
only infers a few ciphertext-plaintext pairs. In addition, as $u$ increases,
the inference precisions decrease slightly. For example, when $u$ increases
from 2 to 512, the inference precision of User004 drops from 30.7\% to 12.8\%.

@@

Informed by the impact of $u$, we set $u$ at 128 for User004, User013 and
User015, and at 256 for User007, User012 and User028, respectively, in order
to evaluate the impact of $r$ and $t$. 
% {\bf Note that the configuration
% exceeds the best one that leads to the highest inference rate. PC: I don't
% quite understand???} 
Our rationale is to increase the coverage of inferred ciphertext-plaintext
pairs, while we use $r$ and $t$ to filter possibly false positives.

@@

Then, we fix $r$ = 10 and evaluate the impact of $t$. 
Figure~\ref{fig:distribution-impact}(c) shows the results. When $t$ is small
(e.g., less than 0.5), we observe that the attack misjudges and filters a
significant number of ciphertext-plaintext pairs, even they are correct. This
introduces {\em false negatives} that reduce the inference rate. As $t$
increases, the number of false negatives decreases.  When $t$ = 1.5, the
inference rates hit the maximum values at 21.2\%, 18.2\%, 10.4\%, 1.2\%,
1.2\%, and 13.5\% for User004, User007, User012, User013, User015, and
User028, respectively. When $t$ further increases to 2, the corresponding
inference rates drop to 20.5\%, 17.1\%, 8.3\%, 1.2\%, 1.0\%, and 11.2\%,
respectively. The reason is that if $t$ is too large, it cannot filter false
positives effectively. For the same reason, the inference precisions for all
users decrease with $t$.  
% The inference rates first  increase with $t$, since the number of false negatives (i.e., misjudge some correctly inferred ciphertext-plaintext pairs in filtering) are reduced.

% implies that the distribution-based attack  returns more incorrect ciphertext-plaintext chunk pairs, which affects attack severity.

@@

We consider the following attack instances for comparison. 
%
\begin{itemize}[leftmargin=*]
\item 
$\tt Baseline$: We re-implement the locality-based attack based on the
parameter configuration suggested in \cite{li17}. Specifically, it infers 5
most frequent ciphertext-plaintext pairs in the first invocation (i.e., to
initialize a set of ciphertext-plaintext pairs for iteration) of frequency
analysis, and 30 in each following invocation (i.e., to iteratively infer ciphertext-plaintext pairs from 
 neighbors).  
\item 
$\tt Distribution$ and $\tt Distribution^S$: We consider two attack instances
of the distribution-based attack, denoted by $\tt Distribution^S$ and ${\tt
Distribution}$, which operate with and without size information,
        respectively (i.e., the superscript $\tt S$ indicates that the attack instance operates with size information). 
        We configure $\tt Distribution^S$ and ${\tt Distribution}$
under the same configuration of  ${\tt Baseline}$. In addition, we choose
$r$ and $t$ in both  $\tt Distribution^S$ and ${\tt Distribution}$ in the following way: for the FSL dataset, we fix $r$ = 10 for
all users, and individually set $t$ = 1.5, 1.2, 1, 1, 0.7, and 0.9 for
User004, User007, User012, User013, User015, and User028, respectively; for
the MS dataset, we also fix $r$ = 10 for all categories, and set $t$ = 2 for
Win7 and Serv-08, and $t$ = 1.6 for Vista-U, Serv-03, and Vista-B, respectively.
This is informed by our tests for optimal configurations of the datasets.   
\item 
$\tt Distribution$-$\tt o$ and $\tt Distribution^S$-$\tt o$:
We consider two additional distribution-based attack instances, denoted by $\tt Distribution$-$\tt o$
and $\tt Distribution^S$-$\tt o$, which apply the same configurations for $r$ and $t$ as with $\tt Distribution$ and $\tt
Distribution^S$, and further use larger $u$ to increase the
coverage of inferred ciphertext-plaintext pairs.  
        Specifically, we configure $u$ in $\tt Distribution$-$\tt o$
and $\tt Distribution^S$-$\tt o$ in the following way:  
        for the FSL
dataset, we apply the same configuration of $u$ in Experiment~1; for the MS
dataset, we set $u$ = 128 for Win7, and $u$ = 30 for Serv-03, Serv-08,
Vista-B, and Vista-U. 
        % Our rationale is to increase
% the inference rate, while we expect  this only leads to a slight
% degradation of the inference precision since the distribution-based attack
% filters a large fraction of false positives. 
\end{itemize}

\begin{figure*}[t]
    \centering
    \begin{tabular}{c@{\hskip 2em}c}
        \multicolumn{2}{c}{\includegraphics[width=.7\textwidth]{pic/legend-fsl-bar.pdf}} \smallskip \\
        \includegraphics[height=2.1in]{pic/distribution-comparison-fsl.pdf} &
        \includegraphics[height=2.1in]{pic/distribution-comparison-ms.pdf} \medskip \\
        {\footnotesize 
        (a) FSL dataset 
        } &
        {\footnotesize
        (b) MS dataset 
        } \\
    \end{tabular}
    \caption{Experiment 2 (Comparison with prior attack): comparison of attack severity for distribution-based attack and locality-based attack.}
    \label{fig:distribution-comparison}
\end{figure*}

% \begin{itemize}[leftmargin=*]
	% \item {\em Distribution-I:} We configure our proposed distribution-based attack with the {\em same} configuration of the baseline above. Informed by Experiment 3, we further choose the distribution-based ranking parameters in the following way: for the FSL dataset, we fix $r$ = 10 for all users, and individually set $t$ = 1.5, 1.2, 1, 1, 0.7, and 0.9 for User004, User007, User012, User013, User015, and User028; for the MS dataset, we fix $r$ = 10 for all categories, and configure $t$ as 2 for Win7 and Serv-08 and as 1.6 for Vista-U, Serv-03, and Vista-B, respectively.

	% \item {\em Distribution-II:} We configure our proposed distribution-based attack with the same ranking configuration of distribution-I, while building on a larger $u$ to infer more chunk pairs. The rationale is to increase inference rate, while we expect the inference precision is degraded slightly as the attack can filter out unreasonable inferences. Specifically, for the FSL dataset, we set $u$ = 128 for User004, User013 and User015, and $u$ = 256 for User007, User012 and User028, respectively; for the MS dataset, we set $u$ = 128 for Win7, and $u$ = 30 for Serv-03, Serv-08, Vista-B, and Vista-U, respectively.
% \end{itemize}

@@

\begin{figure*}[t]
     \centering
    \centering
    \begin{tabular}{c@{\hskip 2em}c}
        \multicolumn{2}{c}{\includegraphics[width=.25\textwidth]{pic/legend-effectiveness.pdf}} \smallskip \\
        \includegraphics[height=2.2in]{pic/distribution-effectiveness-wo-size.pdf} &
	\includegraphics[height=2.2in]{pic/distribution-effectiveness-w-size.pdf} \medskip \\
        {\footnotesize 
        (a) Distribution-based attack without size information  
        } &
        {\footnotesize
        (b) Distribution-based attack with size information 
        } \\
    \end{tabular}
	\caption{Experiment 3 (Attack effectiveness): severity of distribution-based attack in FSL dataset.}
	\label{fig:experiment-distribution-effectiveness}
\end{figure*}

>>>>

在本章中，将给出基于真实世界数据集的评估结果，以证明本文针对加密重复数据删除提出的频率分析攻击方法的严重性与有效性。

@@

本文所使用的真实世界数据集不包数据的实际内容，因此我们模仿基于块哈希的对抗性知识。具体来说，我们在一些快照中使用有序的数据块哈希列表作为辅助信息$\mathbf{A}$和基本事实$\mathbf{M}$。为了模拟加密，我们在$\mathbf{M}$中的每个原始块散列（表示明文）上应用额外的散列函数，并将结果截断为特定于已使用数据集的约定位数。截断的结果模仿$\mathbf{C}$中的密文。对于每个推断的密文 - 明文对$(C,M)$，我们通过在$M$上应用相同的模拟加密并将结果与​​$C$进行比较来验证其正确性。请注意，基于聚类的攻击可以在段级别操作，并推断出密文 - 明文段对$(S_\mathbf{C},S_\mathbf {A})$。在这种情况下，我们检查$(S_\mathbf {C},S_\mathbf{A})$，检查$S_\mathbf{C}$中的每个密文是否完全映射到$S_\mathbf{A}$中的每个明文。

@@

@@

\begin{figure}[!htbp]
    \centering
    \begin{tabular}{p{.48\linewidth}p{.48\linewidth}}
        \multicolumn{2}{c}{\includegraphics[width=.7\textwidth]{legend-fsl-line.pdf}}  \\
        \includegraphics[width=\linewidth]{dis-impact-u-rate.pdf} &
        \includegraphics[width=\linewidth]{dis-impact-u-accuracy.pdf}\\
    \end{tabular}
    \caption{基于分布的攻击实验1-参数$u$的变化对推理结果的影响（$r = 0$；$t \rightarrow \infty$）}
    \label{fig:distribution-impact-u}
\end{figure}

\begin{figure}[!htbp]
    \centering
    \begin{tabular}{p{.48\linewidth}p{.48\linewidth}}
        \multicolumn{2}{c}{\includegraphics[width=.7\textwidth]{legend-fsl-line.pdf}}  \\
        \includegraphics[width=\linewidth]{dis-impact-r-rate.pdf} &
        \includegraphics[width=\linewidth]{dis-impact-r-accuracy.pdf}\\
    \end{tabular}
    \caption{基于分布的攻击实验1-参数$r$的变化对推理结果的影响（User004、User013和User015中$u = 128$，User007、User012和User028中$u = 256$；$t \rightarrow \infty$）}
    \label{fig:distribution-impact-r}
\end{figure}

\begin{figure}[!htbp]
    \centering
    \begin{tabular}{p{.48\linewidth}p{.48\linewidth}}
        \multicolumn{2}{c}{\includegraphics[width=.7\textwidth]{legend-fsl-line.pdf}}  \\
        \includegraphics[width=\linewidth]{dis-impact-t-rate.pdf} &
        \includegraphics[width=\linewidth]{dis-impact-t-accuracy.pdf}\\
    \end{tabular}
    \caption{基于分布的攻击实验1-参数$t$的变化对推理结果的影响（User004、User013和User015中$u = 128$，User007、User012和User028中$u = 256$；$r = 10$）}
    \label{fig:distribution-impact-t}
\end{figure}

@@

The prior work \cite{li17} does not report the inference precision about the attack. We observe that the inference precisions for all users are at a fairly low level (e.g., less than 40\%), except the case of $u = 2$ for User028 that does not introduce any false positives. On the other hand, the inference rate in the special case is about 0.0001\%, meaning that the attack only infers a few ciphertext-plaintext pairs. In addition, as $u$ increases,the inference precisions decrease slightly. For example, when $u$ increases from 2 to 512, the inference precision of User004 drops from 30.7\% to 12.8\%.

@@

Informed by the impact of $u$, we set $u$ at 128 for User004, User013 and User015, and at 256 for User007, User012 and User028, respectively, in order to evaluate the impact of $r$ and $t$.  Our rationale is to increase the coverage of inferred ciphertext-plaintext pairs, while we use $r$ and $t$ to filter possibly false positives.

@@

Then, we fix $r$ = 10 and evaluate the impact of $t$.  Figure~\ref{fig:distribution-impact}(c) shows the results. When $t$ is small (e.g., less than 0.5), we observe that the attack misjudges and filters a significant number of ciphertext-plaintext pairs, even they are correct. This introduces {\em false negatives} that reduce the inference rate. As $t$ increases, the number of false negatives decreases.  When $t$ = 1.5, the inference rates hit the maximum values at 21.2\%, 18.2\%, 10.4\%, 1.2\%, 1.2\%, and 13.5\% for User004, User007, User012, User013, User015, and User028, respectively. When $t$ further increases to 2, the corresponding inference rates drop to 20.5\%, 17.1\%, 8.3\%, 1.2\%, 1.0\%, and 11.2\%, respectively. The reason is that if $t$ is too large, it cannot filter false positives effectively. For the same reason, the inference precisions for all users decrease with $t$.

@@

We consider the following attack instances for comparison.

\begin{itemize}[leftmargin=*]
\item 
$\tt Baseline$: We re-implement the locality-based attack based on the parameter configuration suggested in \cite{li17}. Specifically, it infers 5 most frequent ciphertext-plaintext pairs in the first invocation (i.e., to initialize a set of ciphertext-plaintext pairs for iteration) of frequency analysis, and 30 in each following invocation (i.e., to iteratively infer ciphertext-plaintext pairs from neighbors).  
\item 
$\tt Distribution$ and $\tt Distribution^S$: We consider two attack instances of the distribution-based attack, denoted by $\tt Distribution^S$ and ${\tt Distribution}$, which operate with and without size information, respectively (i.e., the superscript $\tt S$ indicates that the attack instance operates with size information). We configure $\tt Distribution^S$ and ${\tt Distribution}$ under the same configuration of  ${\tt Baseline}$. In addition, we choose $r$ and $t$ in both  $\tt Distribution^S$ and ${\tt Distribution}$ in the following way: for the FSL dataset, we fix $r$ = 10 for all users, and individually set $t$ = 1.5, 1.2, 1, 1, 0.7, and 0.9 for User004, User007, User012, User013, User015, and User028, respectively; for the MS dataset, we also fix $r$ = 10 for all categories, and set $t$ = 2 for Win7 and Serv-08, and $t$ = 1.6 for Vista-U, Serv-03, and Vista-B, respectively. This is informed by our tests for optimal configurations of the datasets.   
\item 
$\tt Distribution$-$\tt o$ and $\tt Distribution^S$-$\tt o$: We consider two additional distribution-based attack instances, denoted by $\tt Distribution$-$\tt o$ and $\tt Distribution^S$-$\tt o$, which apply the same configurations for $r$ and $t$ as with $\tt Distribution$ and $\tt Distribution^S$, and further use larger $u$ to increase the coverage of inferred ciphertext-plaintext pairs.  Specifically, we configure $u$ in $\tt Distribution$-$\tt o$ and $\tt Distribution^S$-$\tt o$ in the following way:  for the FSL dataset, we apply the same configuration of $u$ in Experiment~1; for the MS dataset, we set $u$ = 128 for Win7, and $u$ = 30 for Serv-03, Serv-08, Vista-B, and Vista-U.

\end{itemize}

\begin{figure*}[t]
    \centering
    \begin{tabular}{c}
        \includegraphics[width=.7\textwidth]{pic/legend-fsl-bar.pdf}\\
        \includegraphics[width=.7\textwidth]{pic/distribution-comparison-fsl.pdf} 
    \end{tabular}
    \caption{Experiment 2 FSL dataset  (Comparison with prior attack): comparison of attack severity for distribution-based attack and locality-based attack.}
    \label{fig:distribution-comparison}
\end{figure*}

\begin{figure*}[t]
    \centering
    \begin{tabular}{c}
        \includegraphics[width=.7\textwidth]{pic/legend-fsl-bar.pdf}\\
        \includegraphics[width=.7\textwidth]{pic/distribution-comparison-ms.pdf}\\
    \end{tabular}
    \caption{Experiment 2 MS dataset (Comparison with prior attack): comparison of attack severity for distribution-based attack and locality-based attack.}
    \label{fig:distribution-comparison}
\end{figure*}

@@

\begin{figure*}[t]
     \centering
    \centering
    \begin{tabular}{c}
        \includegraphics[width=.35\textwidth]{pic/legend-effectiveness.pdf}\\
        \includegraphics[width=.7\textwidth]{pic/distribution-effectiveness-wo-size.pdf}
    \end{tabular}
	\caption{Experiment 3 Distribution-based attack without size information  (Attack effectiveness): severity of distribution-based attack in FSL dataset.}
	\label{fig:experiment-distribution-effectiveness}
\end{figure*}

\begin{figure*}[t]
     \centering
    \centering
    \begin{tabular}{c}
        \includegraphics[width=.35\textwidth]{pic/legend-effectiveness.pdf}\\
        \includegraphics[width=.7\textwidth]{pic/distribution-effectiveness-w-size.pdf}
    \end{tabular}
	\caption{Experiment 3 Distribution-based attack with size information (Attack effectiveness): severity of distribution-based attack in FSL dataset.}
	\label{fig:experiment-distribution-effectiveness}
\end{figure*}
